Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
added abstract

---
title: "Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness"
subtitle: "An Analysis of Potential Factors From 2000 to 2021"
author: 
  - Jenny Shen
  - Joyce Xuan
  - Jason Ngo
thanks: "Code and data are available at: https://github.com/jennyshen-playground/women_highest__level_education_20_years.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "hello"
number-sections: true
bibliography: references.bib
---

@@

merged_gss |> group_by(Year) |> count(Happiness) |>
  ggplot(aes(x = Year, y = n, fill = Happiness)) +
  geom_col(position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Womens Happiness over 20 Years",
    x = "Year",
    y = "Count"
  )
```

>>>>

---
title: "Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness"
subtitle: "An Analysis of Potential Factors From 2000 to 2021"
author: 
  - Jenny Shen
  - Joyce Xuan
  - Jason Ngo
thanks: "Code and data are available at: https://github.com/jennyshen-playground/women_highest__level_education_20_years.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper utilizes data from the US General Social Survey to discuss women's level of education from 2000 to 2021. We find that the mean levels of education among surveyed women increased, as did their occupational prestige score and level of happiness. These findings matter as they enable us to understand the importance of women's access to higher education. The rise in occupational prestige scores can enhance economic development, and associates with increased levels of happiness. This suggests that advanced education leads to well-respected careers that generate happiness"
number-sections: true
bibliography: references.bib
---

@@

merged_gss |> group_by(Year) |> filter(!is.na(Happiness)) |> count(Happiness) |>
  ggplot(aes(x = Year, y = n, fill = Happiness)) +
  geom_col(position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Womens Happiness over 20 Years",
    x = "Year",
    y = "Count"
  )
```
